\section{Runtime}
The usage of a runtime is to create a space for the code to
execute. Basically a runtime provides a scope stack for the local
variables to store, and trace the call stack for the function
invoking.

\subsection{Scope Model}
Scopes in \revo\ is only for storing local symbols, which is generally
known as variables. Technically, these symbols are stored in a hash
table, and is referable with their names.

\subsubsection{Free Variables}
Usually, a scope has a parent, this is what we called 'scope nesting'.
When the program requested a variable in a scope, it will firstly
search its own symbol table to see if the variable is defined
locally. If that variable is not found, it will ask its parent for
it. It does this recursively until the variable is found, or it will
raise a '\emph{name-not-found}' exception and interrupt the execution.

A creation of a scope is done by function closure evaluation. A
function closure is usually known as a lambda($\lambda$) in functional
programming. Concisely a closure could be regarded as a composition of
a function, which is a bunch of codes with optional parameters to
accept input and returns a value, and a scope pointer. A lambda will
reserve the pointer to the scope where it is created, and when it
evaluates, a new scope will be created and its parent will be set as
the one it reserves.

So consider this code snippet:
\begin{verbatim}
(define my-lambda       ;; define the lambda with the name 'my-lambda'
  (let ((x 1))          ;; start a local scope and set x to 1
    (lambda () (x))))   ;; create a lambda that return the value of x
(define x 2)            ;; define a global variable x, set it to 2

(display (my-lambda))   ;; it shows 1 instead of 2
\end{verbatim}

Because \verb+my-lambda+ is created under the scope where \verb+x+ is
set to \verb+1+, it will regard this as the parent to search for
variables, no matter what scope it is evaluated at.

The situation I mentioned above is the way how \revo\ deal with
free variables. A free variable, as its name, it not bounded on any
specified value. The concept might be a little complicated to
understand, but I'll explain with a simple example:
\begin{verbatim}
(lambda (a b) (+ a b c))
\end{verbatim}

In this example, it is a anonymous lambda with two parameters \verb+a+
and \verb+b+. When we invoke this lambda, we have to specify two
arguments for it, let's say, \verb+1+ and \verb+2+. In this case,
\verb+1+ will be bounded on \verb+a+, and \verb+2+ will be bounded on
\verb+b+. For the name \verb+c+, the variable it represent is not
designated when the lambda is invoked, so this is what we called 'free
variable'.

\subsubsection{Bounded Variable}
I used a quick way to cope with bounded variables for lambdas. In the
new scope created by a called lambda, I will put a group of variables
with the name of its parameters and the value of the arguments passed
into the symbol table of the scope. So referring its arguments in the
body is right like referring local variables. Actually there's no
concept of local scope in Scheme. Usually, the operator \verb+let+ to
start a local scope is also done by lambda. In the standard template
syntax, \verb+let+ is defined like:

\begin{verbatim}
(define-syntax let
  (syntax-rules ()
    ((let ((name val) ...)
       body ...)
     ((lambda (name ...) body ...)
      val ...))))
\end{verbatim}

So as shown, \verb^(let ((a 41)) (+ a 1))^ is equivalent to
\verb^((lambda (a) (+ a 1)) 41)^, which is not different from calling
a temporary lambda.

\subsection{Call Stack}
Call stack is an important component of a runtime for most programming
language interpreters/compilers. Technically, in a call stack we
record function calls and when a function returns, it will pop the
top, in which stores an address of where the function is called. The
instruction pointer(suppose there is one) will jump to that address to
continue the execution of the program.

In \revo, I didn't record a call stack specifically. When a closure is
invoked, it will directly store the bounded variables with their
arguments passed to the closure in a new scope, then it just simply
evaluate the body. In a imperative programming language, a call will
usually start a completely new scope to store variables. However, in
\revo, there is actually no pure function without a
binding\footnote{Frankly, there is. You can define this kind of
  functions in ruby, as primitive functions in \revo.}. For a closure,
a new scope for it is stacked on the top of the scope where it is
created, another reason that call stack is not necessarily needed is
the functional programming specification. Typically, Scheme doesn't
have any interrupt allowed(ignore \verb+call/cc+), that means, there
is no \verb+break+, \verb+goto+, or even \verb+return+ statements. The
main purpose to keep a call stack is for \verb+return+ statements to
jump among the function stacks.

\subsection{Macro: Template Expansion}
The template system is one of my favorite features in Scheme
programming language. A template in Scheme is usually known as a
\emph{macro}. Macro gives lisp family ultra-magical power to form the
code. Generally, a macro rule holds a pattern of code and a
transformer. To process a macro, a macro matcher will firstly scan the
code and match it with a macro rule using its specified pattern, then
it will apply the transformation.

Unlike a function, a macro take \emph{codes} rather than \emph{values}
as its parameters. The codes passed to it will not be evaluated before
the macro expansion. Therefore it has meta-power to control the code.

Macros syntax in Scheme is like:
\begin{verbatim}
(define-syntax my-if (else)
  (syntax-rules
    ((my-if cond body ...)
     (if cond (begin body ...) nil))
    ((my-if cond if-part ... else else-part ...)
     (if cond (begin if-part ...) (begin else-part ...)))))
\end{verbatim}

So when I call it with \verb+(my-if 1 'a else 'b)+, it will
be transformed to \verb+(if 1 (begin 'a) (begin 'b))+. This
process will be done before the final code evaluation. My
implementation is slightly different. Since \revo\ is an interpreter
than a compiler, the compile-time and the run-time is combined
together. I deal with macros as long as I deal with other callable
objects in the run-time.

The matcher and the transformer\footnote{In \revo\ it is called as a
template.} are separate parts. When a macro is found called somewhere,
the macro processor will invoke the bunch of matchers for that macro;
then it will return the one that matches the pattern. The matcher scan
pattern and relate different parts of code with the names specified in
the macro definition. This relation table will be passed to the
corresponding transformer, and the transformer restore the snippet of
code with the transformation rules defined according to the
table. Finally the snippet generate will replace the original macro
calling, and will be evaluated as a regular code.

\subsubsection{Unhygienic Macro}
In a programming language that has unhygienic macro support, it is
possible to poison the external binding from macro
expansion. Unhygienic macro is a kind of black magic that you can use
its power to construct things beyond, but if it is mishandled, its will
cause unexpected results.

Macros in Common Lisp is unhygienic. \RFIVERS\ specified that
macros in Scheme should be hygienic. In order to give programmer more
freedom, I added an option in \revo's implementation to support
unhygienic macros.

Unhygienic macro is relative easy to implement. All need to do is just
substitute the names with it's


\subsubsection{Hygienic Macro}
\url{http://lifegoo.pluskid.org/?p=418}
In opposite to unhygienic macros, hygienic macro has no side effect

In specification document, it states:
\begin{quote}
If a macro transformer inserts a binding for an identifier (variable
or keyword), the identifier will in effect be renamed throughout its
scope to avoid conflicts with other identifiers.
\end{quote}
\begin{flushright}
--\href{http://www.schemers.org/Documents/Standards/R5RS/HTML/r5rs-Z-H-7\.html\#\%\_sec\_4\.3}{\RFIVERS}
\end{flushright}

That means a

